Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006,hiester_2014,mostaghimi_2016}. %The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}. 
In the simulations shown in this section, mesh grid adapts as a response to oscillations of phase saturations with: (a) minimum value for length of elements of 0.05 unit-length, (b) maximum number of nodes of 5$\times$10$^{4}$, and (c) prescribed interpolation error estimate of 10$^{-2}$.

>>>>

The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006,hiester_2014,mostaghimi_2016}. %The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}. 
In the simulations shown in this section, mesh grid adapts as a response to oscillations of phase saturations with: (a) minimum value for length of elements of 0.05 unit-length, (b) maximum number of nodes of 5$\times$10$^{4}$, and (c) prescribed interpolation error estimate of 10$^{-2}$.
